---
title: "Alcohol vs Seat choice"
author: "Leonel D. Bautista"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

# Introduction

We will be looking into the DavisData data set that is included with tidyverse to see if there is and correlation between alcohol consumption and the chosen seat.     

$H_0$ There is no difference in the data between alcohol and seat.     

$H_A$ There is difference in the data between alcohol and seat.    

```{r}
glimpse(davisdata)
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

# Methods   

Looking at the data using glimpse() we can see that Alcohol is a continuous numerical and seat is a regular categorical. This problem is a numerical categorical comparison so we will use the Num~Cat helper file in CandP. We will also use the my tricks to factor the categorical data using dyplr. We will show our graphical results using ggplot2, numerical with favstats, and run inferential tests with an anova because we have more than two categories and then a TukeyHSD to find where the differences are in our data.   

## Numerical Summarys 

## Inferential Tests

## Conclusions


