---
title: "Alcohol vs Seat choice"
author: "Leonel D. Bautista"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

# Introduction

We will be looking into the DavisData data set that is included with tidyverse to see if there is and correlation between alcohol consumption and the chosen seat.     

$H_0$ There is no difference in the data between alcohol and seat.     

$H_A$ There is difference in the data between alcohol and seat.    

```{r}
glimpse(davisdata)
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

# Methods   

Looking at the data using glimpse() we can see that Alcohol is a continuous numerical and seat is a regular categorical. This problem is a numerical categorical comparison so we will use the Num~Cat helper file in CandP. We will also use the my tricks to factor the categorical data using dyplr. We will show our graphical results using ggplot2, numerical with favstats, and run inferential tests with an anova because we have more than two categories and then a TukeyHSD to find where the differences are in our data.   

# Results      

## Descriptive Results   

### Graphical Descriptive Results   

``` {r include = TRUE, echo = FALSE}
ggplot(data = davisdata, aes(x = Seat, y = alcohol) ) +
geom_boxplot (notch=FALSE,outlier.colour = "red",outlier.size = 2, fill = "darkgray") +
stat_boxplot (geom ='errorbar') +
labs (x = "Seat", y = "Alcohol Consumed", title = "Alcohol vs Seat Choice") +
theme (plot.title = element_text(hjust = 0.5, size = 16) )
```

In this analysis, it is evident that the back seats exhibit a notable discrepancy in alcohol consumption compared to the front and middle seats. The median alcohol consumption in the back seats nearly aligns with the upper quartile (Q4) measure in the front seats. Furthermore, the interquartile range (IQR) of the back seats surpasses the median of both the front and middle seats.   

Additionally, the middle seats show a slight elevation in alcohol consumption compared to the front seats, as evidenced by a higher median and a greater number of outliers. With a more comprehensive assessment, it is likely that the front and middle seats would demonstrate a closer similarity in alcohol consumption patterns.   

## Numerical Summarys 

``` {r include = TRUE, echo = FALSE}
favstats(alcohol~Seat,data=davisdata)
```

The median and mean values for the back seats category exhibit a significant elevation, surpassing what could be attributed to random fluctuations. Moreover, given the sample size (n > 30), we would anticipate relatively smaller variations compared to what is actually observed.      

Additionally, the $\sigma$ in the back seats category is notably greater, exceeding twice the magnitude seen in the other two categories.     

## Inferential Tests

``` {r include = TRUE, echo = FALSE}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We see here that there is a significant difference somewhere in the data, p = 0.000116 (<0.05).     

```{r}
plot(TukeyHSD(model1,conf.level = 0.99))
```

We see here in the TukeyHSD the only similar categories are the Middle and Front. The back differs strongly with front and the middle and we can say with a 99% confidence that there is a correlation between Alcohol and Seat.     

## Conclusions

From various metrics, it is evident that individuals seated in the back consume a significantly higher amount of alcohol compared to those in other categories. Both graphical, numerical, and inferential analyses consistently demonstrate a substantial divergence in the data across these categories. With a confidence level of 99%, we assert that there exists a robust correlation between back seat occupants and the remaining categories. It is imperative to scrutinize the data collection methodology to confirm that it does not rely on a convenience sample and to ensure the absence of collection biases, such as non-response bias.   

